---
title: "Soil Incubations of Soil Contaminated with Legacy Pesticides"
author: "CK"
date: "15/06/2020"
output: 
 bookdown::html_document2:
   toc: yes
   fig_caption: yes
   number_sections: false
editor_options: 
  chunk_output_type: console
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
  encoding=encoding,
  output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
  
---

```{r raw_peakdata_standards_dieldrin, message=FALSE, echo = FALSE, warning = FALSE}
library(reshape2)
library(lubridate)
library(tidyverse)

dataCO2 <- read.csv("dataCO2.csv", header = TRUE, row.names=NULL)
dataCO2 <-dataCO2 %>%  dplyr::mutate_all(type.convert) %>% dplyr::mutate_if(is.factor, as.character) 
```


# Data overview
```{r dataoverview, echo=FALSE, fig.width=10, fig.asp=0.4, message=FALSE, echo = FALSE, warning = FALSE, cache=TRUE, include=FALSE}
library(hrbrthemes)
library(ggpubr)
library(tidyverse)
library(rstatix)

dataCO2$Treatment[dataCO2$Treatment == "AutoclavedControl"] <- "Heat"
dataCO2 <- dataCO2 %>% mutate(Week_int = case_when(Week == "T02" ~ 02,
                              Week == "T04" ~ 04,
                              Week == "T06" ~ 06,
                              Week == "T08" ~ 08,
                              TRUE ~0) )

dataCO2 <- dataCO2 %>% convert_as_factor(Samples, Treatment, Replicate, Week, Category)
#order factors
dataCO2$Treatment <- factor(dataCO2$Treatment, levels=c("Control", "Lime", "PoultryLitter", "Biochar", 
                                                                "CitricAcid", "Inositol", "SodiumFormate", "SodiumAcetate",
                                                                "FumaricAcid", "Heat","H2O2"))
#dataCO2$Week <- factor(dataCO2$Week, levels=c("T02","T04", "T06", "T08"))
str(dataCO2)

# outliers
dataCO2 %>%
  group_by(Week) %>% dplyr::filter(Week != "T08") %>%
  rstatix::identify_outliers(µgCO2.Cgsoilday) %>% select(Week,Treatment, µgCO2.Cgsoilday, is.outlier, is.extreme)
```


```{r lineplot, fig.width=8, fig.asp=0.7,  message=FALSE, echo = FALSE, cache=FALSE, warning = FALSE, fig.cap="Dieldrin concentrations (log) across time. Error bars show the standard error of the mean of four replicates."}
str(dataCO2)
dataCO2  %>% ggpubr::ggline(data = ., x = "Week_int", y = "µgCO2.Cgsoilday", ylab = "µgCO2.Cgsoilday", add = c("mean_se"), color = "Treatment", palette = "simpsons") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal")

#l01 <- data  %>% filter(SampleNo != 4 ) %>% ggline(data = ., x = "Week_int", y = "T0_Diff", add = c("mean_se"), color = "Treatment", palette = "simpsons") + rotate_x_text(angle = 45) + stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal")



pdf(NULL)
g1 <- ggpubr::ggarrange(l0, nrow = 1, ncol=1, common.legend = TRUE)
x = dev.off()
g1

```
<br/>
 
```{r line2, echo=FALSE, fig.width=8, fig.asp=1,  message=FALSE, cache=TRUE, warning = FALSE, fig.cap="Residues remaining since T0 in percent for two sets of treatments including the control (a,b). Error bars show the standard error of the mean of four replicates. Dieldrin concentrations (µg/g) over time."}

l1 <- data  %>% filter(SampleNo != 4 ) %>% filter(Week != "T52" ) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T0_Diff", ylab = "Residue remaining since T0 (%)", add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE)  + ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") + ggpubr::rotate_x_text(angle = 45) 

s1 <- data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week != "T52" ) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE ) + ggpubr::rotate_x_text(angle = 45)

l2 <-   data  %>% filter(SampleNo != 4 ) %>% filter(Week != "T52" ) %>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T0_Diff", ylab = c("Residue remaining since T0 (%)"), add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE) +  ggpubr::rotate_x_text(angle = 45)+ ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") 

s2 <-  data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week != "T52" )%>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE) + ggpubr::rotate_x_text(angle = 45)


pdf(NULL)
x = dev.off()
ggpubr::ggarrange(ncol =1, nrow=2, ggarrange(l1, s1, ncol = 2, nrow =1, common.legend = TRUE), ggarrange(l2, s2, ncol =2, nrow =1, common.legend = TRUE), labels = "auto" ) 

```
<br/>

```{r line23952, echo=FALSE, fig.width=8, fig.asp=1,  message=FALSE, cache=TRUE, warning = FALSE, fig.cap="Residues remaining since T39 (9 month) in percent for two sets of treatments including the control (a,b). Error bars show the standard error of the mean of four replicates. Dieldrin concentrations (µg/g) over time."}
l1 <- data  %>% filter(SampleNo != 4 ) %>% filter(Week %in% c("T39", "T52" )) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T39_Diff", ylab = c("Residue remaining since T39 (%)"), add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE)  + ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") + ggpubr::rotate_x_text(angle = 45) 

s1 <- data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week %in% c("T39", "T52" )) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE ) + ggpubr::rotate_x_text(angle = 45)

l2 <-   data  %>% filter(SampleNo != 4 ) %>% filter(Week %in% c("T39", "T52" )) %>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T39_Diff", ylab = c("Residue remaining since T39 (%)"),  add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE) +  ggpubr::rotate_x_text(angle = 45)+ ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") 

s2 <-  data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week %in% c("T39", "T52" ))%>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE) + ggpubr::rotate_x_text(angle = 45)

pdf(NULL)
x = dev.off()
ggpubr::ggarrange(ncol =1, nrow=2, ggarrange(l1, s1, ncol = 2, nrow =1, common.legend = TRUE), ggarrange(l2, s2, ncol =2, nrow =1, common.legend = TRUE), labels = "auto" ) 

```
<br/>

# Dieldrin loss
```{r dloss, echo=FALSE, fig.width=10, fig.asp=2, include=TRUE, fig.cap="Residues loss in percent. Error bars show the standard error of the mean of four replicates. Letters show differences of the mean after multiple comparison tests (dunn test, holm correct *p* value)."}
library(ggpubr)
library(agricolae)

#Loss plot for week 39
df <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T39" )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p1 <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T39" ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", facet.by = "Week", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%)") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 15) + geom_hline(yintercept = 0, linetype = 2)  + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)
#+ ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "Control", hide.ns = TRUE)

#Loss plot for week 52
df <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p2 <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", facet.by = "Week", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%)") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 23) + geom_hline(yintercept = 0, linetype = 2)  + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)
#+ ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "Control", hide.ns = TRUE)

## loss plot from week 52 since week 39 
df <-  data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" )
kr.test <- with(df,kruskal(loss39,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p3 <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss39",  fill = "Treatment", palette = "simpsons", facet.by = "Week", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%) T39 - T52") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 23) + geom_hline(yintercept = 0, linetype = 2) + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)


## loss plot from week 39 using average values of T0 and T16 with dunn test labels
# Do not include - not sure about interpretation
df1 <- data.frame(T0T16_avg = ((T0$Dieldrin + T16$Dieldrin) / 2), data %>% filter(Week == "T39") %>% select(Dieldrin), data %>% filter(Week == "T52") %>% select(Dieldrin), data %>% filter(Week == "T0") %>% select(Treatment), data %>% filter(Week == "T0") %>% select(SampleNo)  ) %>% rename(T39 = Dieldrin) %>%  rename(T52 = Dieldrin.1) 

df <-  df1 %>% dplyr::mutate(loss = (T0T16_avg - T39) / T0T16_avg *100 )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
#dunntest.df <- rstatix::dunn_test(df, loss ~ Treatment)
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p4 <- df1 %>% dplyr::mutate(loss = (T0T16_avg - T39) / T0T16_avg *100 ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%) T0T16_avg - T39") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 10) + geom_hline(yintercept = 0, linetype = 2) + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)

#pwc <- df %>% mutate(loss = (T0T16_avg - T52) / T0T16_avg *100 ) %>% 
#  dunn_test(loss ~ Treatment, p.adjust.method = "holm") 

## loss plot from week 52 using average values of T0 and T16 with dunn test labels
# Do not include - not sure about interpretation
df1 <- data.frame(T0T16_avg = ((T0$Dieldrin + T16$Dieldrin) / 2), data %>% filter(Week == "T39") %>% select(Dieldrin), data %>% filter(Week == "T52") %>% select(Dieldrin), data %>% filter(Week == "T0") %>% select(Treatment), data %>% filter(Week == "T0") %>% select(SampleNo)  ) %>% rename(T39 = Dieldrin) %>%  rename(T52 = Dieldrin.1) 

df <-  df1 %>% dplyr::mutate(loss = (T0T16_avg - T52) / T0T16_avg *100 )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p5 <- df1 %>% mutate(loss = (T0T16_avg - T52) / T0T16_avg *100 ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%) T0T16_avg - T52") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 22) + geom_hline(yintercept = 0, linetype = 2) + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)+ ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "Control", hide.ns = TRUE)


ggarrange(p1, p2, p3, ncol = 1)



```


```{r ordinarymodels, message=FALSE, echo = TRUE, warning = FALSE, include=FALSE}

intercept <- 1
df <- data %>% filter(Week != "T0") %>% filter(SampleNo != 4 )
mod2 <- lm(I((T0_Diff) - intercept) ~  Treatment, data = df)
summary(mod2)
car::Anova(mod2, type = 3)

intercept <- data %>% filter(SampleName != "t0_4.run" ) %>% summarise(meanD = mean(Dieldrin))
intercept <- intercept$meanD
df <- data %>% filter(SampleName != "t0_4.run" )
mod3 <- lm(I(Dieldrin - intercept) ~ Treatment, data = df)
summary(mod3)
car::Anova(mod2, type = 3)

```

# Some awesome summary diagnostics
https://www.datanovia.com/en/lessons/repeated-measures-anova-in-r/
```{r rmanova, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=TRUE}
# Normality
library(rstatix)
data %>% filter(SampleName != "t0_4.run" ) %>% 
  group_by(Week) %>%
   rstatix::shapiro_test(Dieldrin)

# outliers
data  %>%
  group_by(Week) %>%
  rstatix::identify_outliers(Dieldrin) %>% select(Week,Treatment, Dieldrin, is.outlier, is.extreme)

# Summary mean and sd
data %>% filter(SampleName != "t0_4.run" ) %>%
  group_by(Week) %>%
  get_summary_stats(Dieldrin, type = "mean_sd")
```
Transform dieldrin values to improve distribution in order to meet normality assumption
remove 1 extreme outlier sample (Control, 1.33µg/g dieldrin)

```{r rmanova2, echo=FALSE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=TRUE}
data_fltrd %>%
  group_by(Week) %>%
   rstatix::shapiro_test(Dieldrin_trans) 

data_fltrd %>%
  group_by(Week) %>%
   rstatix::shapiro_test(Dieldrin) 
```
Go with log transform for now

```{r rmanova3, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=TRUE}
library(rstatix)

res.aov <- anova_test(data = data_fltrd, dv = Dieldrin_trans, between = c(Week, Treatment))

rstatix::get_anova_table(res.aov)

pwc <- data_fltrd %>%
  pairwise_t_test(
    Dieldrin_trans ~ Week, paired = FALSE,
    p.adjust.method = "bonferroni"
    )

bxp <- ggboxplot(data_fltrd, x = "Week", y = "Dieldrin_trans", add = "point")

pwc <- pwc %>% add_xy_position(x = "Week")
bxp <- bxp + 
  stat_pvalue_manual(pwc) +
  labs(
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)
  )
bxp
```

## Some more summary stats, this time including Treatment
```{r rmanova4, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=FALSE}
data_fltrd %>%
  group_by(Treatment, Week) %>%
  get_summary_stats(Dieldrin_trans, type = "mean_sd")

data_fltrd %>%
  group_by(Treatment, Week) %>%
  identify_outliers(Dieldrin) %>% dplyr::select(Week, Treatment, Dieldrin, is.outlier, is.extreme)

ggqqplot(data_fltrd, "Dieldrin_trans", ggtheme = theme_bw()) +
  facet_grid(Week ~ Treatment, labeller = "label_both")
```

## A repeated measures ANOVA (this is not valid as I used replicates as individuals)
There were no individual soils that were treated differently but wanted to see what happens if we assume that each replicate was the same individual
```{r rmanova5, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE}
data_sel <- data %>% dplyr::select(Replicate, Treatment, Week, Dieldrin) %>% as_tibble()
anova_test(  data = data_sel, dv = Dieldrin, wid = Replicate,
  within = c(Treatment, Week) )

```


# LME models
```{r lme, fig.width=10, fig.asp= 1, message=FALSE, echo = TRUE, warning = FALSE}
library(lme4)
library(lmerTest)
library(car)
library(rafalib)
library(visreg)
library(sjPlot)
library(sciplot)
library(nlme)
library(MASS)
library(ggpubr)
theme_set(theme_bw())


M <- gls(log(Dieldrin) ~ Treatment, data = data_fltrd)
M0 <- lme(log(Dieldrin)  ~ Treatment,  random =~ 1 | SampleNo, data = data_fltrd)
M1 <- lme(log(Dieldrin)  ~ Treatment,  random =~ 1 | Week_int/SampleNo, data = data_fltrd)
M2 <- lme(log(Dieldrin)  ~  Treatment,  random =~ 1 | SampleNo/Week_int, data = data_fltrd)
M3 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | SampleNo/InjectionDate, data = data_fltrd)
M4 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | InjectionDate, data = data_fltrd)
M5 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | InjectionDate/SampleNo, data = data_fltrd)
M6 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | Week_int/InjectionDate, data = data_fltrd)
M7 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | Week_int, data = data_fltrd)
anova(M, M0, M1, M2, M3, M4, M5, M6, M7)

M <- gls(log1p(Dieldrin) ~ Treatment + Week, data = data)
M0 <- lme(log1p(Dieldrin)  ~ Treatment + Week,  random =~ 1 | SampleNo, data = data)
M1 <- lme(log1p(Dieldrin)  ~ Treatment + Week,  random =~  1 | InjectionDate, data = data)
#M2 <- lme(log1p(Dieldrin_cor)  ~ Treatment + Week,  random =~  1 | Week_int, data = data)
anova(M, M0, M1)


M1 <-  lme(log(Dieldrin)  ~ Treatment,  random =~  1 | Week_int/InjectionDate, data = data_fltrd)

E <- resid(M1, type = 'normalized') 
shapiro.test(E)
E <- data.frame(E = E)

Ehist <- ggplot(E, aes(x=(E))) +  geom_histogram(color="black", fill="black") + ggtitle("Residuals Histogram")

F0 <- fitted(M1)
df <- data.frame(F0 = F0, E = E, Treatment = data_fltrd$Treatment, Week_int = data_fltrd$Week_int, Dieldrin = data_fltrd$Dieldrin_trans) 

residscatter <- ggscatter(data= df, x = "F0", y = "E", xlab = "Fitted values", ylab = "Residuals") + ggtitle("Residuals distribution")

D_scatter <- ggscatter(data= df, x = "Dieldrin", y = "E", xlab = "Dieldrin_trans", ylab = "Residuals", add = ("reg.line"))

trt_bxp <- ggboxplot(data= df, x = "Treatment", y = "E", xlab = "Treatment fitted values", ylab = "Residuals", add = ("jitter"))+ rotate_x_text(angle = 45)

Week_scatter <- ggscatter(data= df, x = "Week_int", y = "E", xlab = "Week_int", ylab = "Residuals", add = ("reg.line"))

ggarrange(Ehist, residscatter, D_scatter, Week_scatter, trt_bxp, nrow = 3, ncol = 2)
```
  
## Auto-correlation plot 
```{r}
acf(E)
```

```{r, message=FALSE, echo = FALSE, warning = FALSE}
summary(M1)
```
