---
title: "Soil Incubations of Soil Contaminated with Legacy Pesticides"
author: "CK"
date: "15/06/2020"
output: 
 bookdown::html_document2:
   toc: yes
   fig_caption: yes
   number_sections: false
editor_options: 
  chunk_output_type: console
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
  encoding=encoding,
  output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
  
---

```{r raw_peakdata_standards_dieldrin, message=FALSE, echo = FALSE, warning = FALSE}
library(reshape2)
library(lubridate)
library(tidyverse)

Sample_Peaks <- read.csv("peak_area_samples.csv", header = TRUE, row.names=NULL)
Sample_Peaks1 <- Sample_Peaks %>%  filter(!is.na(GCArea_DDD))
Sample_Peaks2 <- Sample_Peaks %>%  filter(is.na(GCArea_DDD))
  
Standards_Peaks <- read.csv("peak_area_standards.csv", header = TRUE, row.names=NULL)
Standards_Peaks_Donly <- read.csv("peak_area_standards_Donly.csv", header = TRUE, row.names=NULL)
#remove outlier
Standards_Peaks <- Standards_Peaks[-39,]

#Skip this step and only use the dieldrin calcs with corrected standards 
# calculate dieldrin concentrations from d/ddd ratios (internal standard) #
#create standard ratios and regression coefficients 
#ratio_df <- Standards_Peaks %>% mutate(InjectionDate = lubridate::dmy(Standards_Peaks$InjectionDate))  %>% mutate("0.47" = D0.47 / DDD0.47)  %>% mutate("0.094" = D0.094 / DDD0.094) %>% mutate("0.0094" = D0.0094 / DDD0.0094) %>% select(InjectionDate,"0.47", "0.094", "0.0094") %>%   reshape2::melt(data = . , measure.vars = c("0.47", "0.094","0.0094"))
#make variable numeric
#mapping <- c("0.47" = 0.47, "0.094" = 0.094, "0.0094" = 0.0094)
#ratio_df$variable <- mapping[ratio_df$variable]

#model regression for each injection date and create table with coefficients
#require(broom)
#intercept_slope <- ratio_df %>%   group_by(InjectionDate) %>%   nest() %>% mutate(model = map(data, ~lm(variable ~ value, data = .) %>%  tidy)) %>%  unnest(model) %>%  select(InjectionDate,estimate, term) %>%  pivot_wider(names_from = term, values_from = estimate) 

# get sample ratios and add the regression results and dieldrin concentrations
# Sample_Peaks1 <- Sample_Peaks1 %>% mutate(InjectionDate = lubridate::dmy(Sample_Peaks1$InjectionDate)) %>%inner_join(intercept_slope, by = c("InjectionDate" = "InjectionDate")) %>% mutate(Splratio = GCArea_Dieldrin / (GCArea_DDD * 0.98)) %>%mutate(Dieldrin = (Splratio * value + `(Intercept)`) * 12) %>% dplyr::select(-value, -`(Intercept)`)


#Do the same again but with ratios corrected for changes in means (standards have changed over time)
#create standard ratios and regression coefficients
ratio_cor_df <- Standards_Peaks %>%
  mutate(InjectionDate = lubridate::dmy(Standards_Peaks$InjectionDate))%>%
  mutate("0.47" = ( ( (DDD0.47 / mean(DDD0.47)) - (D0.47 /  mean(D0.47))+1 )) * (D0.47 / DDD0.47) )  %>%
  mutate("0.094" = ( ( (DDD0.094 / mean(DDD0.094)) - (D0.094 /  mean(D0.094))+1 )) * (D0.094 / DDD0.094) ) %>%
  mutate("0.0094" = ( ( (DDD0.0094 / mean(DDD0.0094)) - (D0.0094 /  mean(D0.0094))+1 )) * (D0.0094 / DDD0.0094) ) %>%
  select(InjectionDate,"0.47", "0.094", "0.0094") %>%
  melt(data = . , measure.vars = c("0.47", "0.094","0.0094"))
#make variable numeric
mapping <- c("0.47" = 0.47, "0.094" = 0.094, "0.0094" = 0.0094)
ratio_cor_df$variable <- mapping[ratio_cor_df$variable]
#model regression for each injection date and create table with coefficients
require(broom)
intercept_slope <- ratio_cor_df %>% 
  group_by(InjectionDate) %>% 
  nest()%>%
  mutate(model = map(data, ~lm(variable ~ value, data = .) %>% 
                       tidy)) %>% 
  unnest(model) %>% 
  select(InjectionDate,estimate, term) %>% 
  pivot_wider(names_from = term, values_from = estimate) 

#get sample ratios and add the regression results and dieldrin concentrations
Sample_Peaks1 <- Sample_Peaks1 %>% 
  mutate(InjectionDate = lubridate::dmy(Sample_Peaks1$InjectionDate))  %>%
  inner_join(intercept_slope, by = c("InjectionDate" = "InjectionDate")) %>% mutate(Splratio = GCArea_Dieldrin / (GCArea_DDD * 0.98)) %>% mutate(Dieldrin = (Splratio * value + `(Intercept)`) * 12) %>% dplyr::select(-value, -`(Intercept)`) %>% dplyr::select(-Splratio)
# 1 ml analysed of 12 ml extracts


# Calculate dieldrin concentrations from those measurements where no internal standard was available #
std_df <- Standards_Peaks_Donly %>%
  mutate(InjectionDate = lubridate::dmy(Standards_Peaks_Donly$InjectionDate))  %>%
  mutate("0.47" = D0.47)  %>%
  mutate("0.094" = D0.094 ) %>%
  mutate("0.0094" = D0.0094) %>%
  select(InjectionDate,"0.47", "0.094", "0.0094") %>%
    reshape2::melt(data = . , measure.vars = c("0.47", "0.094","0.0094"))
#make variable numeric
mapping <- c("0.47" = 0.47, "0.094" = 0.094, "0.0094" = 0.0094)
std_df$variable <- mapping[std_df$variable]
#model regression for each injection date and create table with coefficients
require(broom)
intercept_slope <- std_df %>% 
  group_by(InjectionDate) %>% 
  nest() %>%
  mutate(model = map(data, ~lm(variable ~ value, data = .) %>% 
                       tidy)) %>% 
  unnest(model) %>% 
  select(InjectionDate,estimate, term) %>% 
  pivot_wider(names_from = term, values_from = estimate) 

Sample_Peaks2 <- Sample_Peaks2 %>% 
  mutate(InjectionDate = lubridate::dmy(Sample_Peaks2$InjectionDate))  %>%
  inner_join(intercept_slope, by = c("InjectionDate" = "InjectionDate")) %>% 
  mutate(Dieldrin = (GCArea_Dieldrin * value + `(Intercept)`) * 12) %>% dplyr::select(-value, -`(Intercept)`)
# 1 ml analysed of 12 ml extracts

# Combine Sample_peaks1 and 2 (So dieldrin values from internal standards plus earlier measurments without internal standards)

Sample_Peaks <- rbind(Sample_Peaks1, Sample_Peaks2)

#Final output for graphing
```


# Data overview
```{r dataoverview, echo=FALSE, fig.width=10, fig.asp=0.4, message=FALSE, echo = FALSE, warning = FALSE, cache=TRUE, include=FALSE}
library(hrbrthemes)
library(ggpubr)
library(tidyverse)
library(rstatix)

data <- Sample_Peaks %>% rename(Week = "TWeeks") %>% filter(SampleName != "t0__40_e2c1001")
data$Treatment[data$Treatment == "AutoclavedControl"] <- "Heat"
data <- data  %>% filter(Treatment != "ref_garretto")
data <- data %>% mutate(Week_int = case_when(Week == "T16" ~ 16,
                              Week == "T39" ~ 39,
                              Week == "T52" ~ 52,
                              TRUE ~0) )

data <- data %>% convert_as_factor(SampleID, SampleNo, Replicate)
#order factors
data$Treatment <- factor(data$Treatment, levels=c("Control", "Lime", "PoultryLitter", "Biochar", 
                                                                "CitricAcid", "Inositol", "SodiumFormate", "SodiumAcetate",
                                                                "FumaricAcid", "Heat","H2O2"))
#data$Category <- factor(data$Category, levels=c("Control","AGamend", "Csubstrate", "Stress"))
data$Week <- factor(data$Week, levels=c("T0","T16", "T39", "T52"))
data  <- data %>% arrange(Week, SampleNo)
data$Dieldrin_trans <- log(data$Dieldrin)

# outliers
#data %>%
#  group_by(Week) %>%
#  rstatix::identify_outliers(Dieldrin) %>% select(Week,Treatment, Dieldrin, is.outlier, is.extreme)
#identified sample 04 (control) as extreme outlier

T0 <- data %>% filter(Week == "T0")
T16 <- data %>% filter(Week == "T16")
T39 <- data %>% filter(Week == "T39")
T52 <- data %>% filter(Week == "T52")
data$T0_Diff <- (data$Dieldrin / T0$Dieldrin) *100
data$T39_Diff <- (data$Dieldrin / T39$Dieldrin) *100
data$loss <- (T0$Dieldrin - data$Dieldrin) / T0$Dieldrin *100
data$loss39 <- (T39$Dieldrin - data$Dieldrin) / T39$Dieldrin *100
data_fltrd <- data %>% filter(SampleName != "t0_4.run")

intercept <- mean(T0$Dieldrin[-4])
mod2 <- lm(I((Dieldrin) - intercept) ~  Week, data = data_fltrd)
summary(mod2)
car::Anova(mod2, type = 3)

df <- data %>% filter(Week != "T0")
#shapiro.test(df$T0_Diff)
#mod1 <- lm(log1p(T0_Diff) ~ Week, data = df)
#summary(mod1)
#car::Anova(mod, type = 3)
intercept <- 1
mod2 <- lm(I((T0_Diff) - intercept) ~  Week, data = df)
summary(mod2)
car::Anova(mod2, type = 3)

intercept <- mean(T0$Dieldrin[-4])
mod <- lm(Dieldrin_trans ~  Treatment*Week, data = data_fltrd)
summary(mod)
car::Anova(mod2, type = 3)

```

```{r boxplots1, echo=FALSE, fig.width=10, fig.asp=0.8, message=FALSE, echo = FALSE, warning = FALSE, cache=TRUE, fig.cap="Boxplots of dieldrin concentrations and dieldrin concentrations relative to start of experiment (T0), including histograms."}
p1.1 <- data %>% filter(Week != "T0") %>% filter(SampleNo != 4 ) %>% ggboxplot(data = ., x = "Week", y = "T0_Diff", ylab = "Residue remaining since T0 (%)",  add = "jitter", fill = "Week", palette = "simpsons", xlab = FALSE) +  rotate_x_text(angle = 45) + stat_compare_means( method = "kruskal")   + scale_fill_manual(values=c("cornflowerblue", "azure4", "burlywood3" )) + ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "T16", hide.ns = TRUE)

p2.1 <- data  %>% filter(SampleNo != 4 ) %>% filter(Week != "T0") %>% gghistogram(data =., x= "T0_Diff", fill = "Week", facet.by = "Week",add = "mean", rug = TRUE) + scale_fill_manual(values=c("cornflowerblue", "azure4", "burlywood3")) + scale_color_manual(values=c("cornflowerblue", "azure4", "burlywood3"))

p1.2 <- data  %>% filter(SampleName != "t0_4.run" ) %>% ggboxplot(data = ., x = "Week", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = "jitter", fill = "Week", palette = "simpsons", xlab = FALSE) + rotate_x_text(angle = 45) + ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "T0", hide.ns = TRUE) + stat_compare_means(label.y = 1.25, method = "kruskal") 

p2.2 <- data  %>% filter(SampleNo != 4 ) %>% gghistogram(data =., x= "Dieldrin", fill = "Week", palette = "simpsons", facet.by = "Week",add = "mean", rug = TRUE)

ggarrange(p1.2, p2.2, p1.1, p2.1, ncol = 2, nrow = 2)

```
<br/>
```{r boxpl2, echo=FALSE, fig.width=10, fig.asp=1.25,  message=FALSE, cache=TRUE, warning = FALSE, fig.cap="Boxplots of dieldrin concentrations by treatment, week/treatment and treatment/week."}
p1 <- data %>% filter(SampleName != "t0_4.run" ) %>% ggboxplot(data = ., x = "Treatment", y = "Dieldrin",  ylab = "Dieldrin (µg/g)", add = "jitter", fill = "Treatment", palette = "simpsons", xlab = FALSE) + rotate_x_text(angle = 45) + stat_compare_means(label.y = 1.25, method = "kruskal")   # Add global annova p-value

p2 <- ggboxplot( data_fltrd, x = "Treatment", y = "Dieldrin_trans",  ylab = "Dieldrin (log)", fill = "Week", palette = "simpsons") + rotate_x_text(angle = 45)

p3 <- ggboxplot( data_fltrd, x = "Week", y = "Dieldrin_trans", ylab = "Dieldrin (log)", fill = "Treatment", palette = "simpsons")+ rotate_x_text(angle = 45)

ggarrange(ggarrange(p1, p3,ncol = 1, common.legend = TRUE), p2, ncol = 1, heights = c(0.66, 0.33))

```
<br/>
```{r T0T16avg, echo=FALSE, fig.width=8, fig.asp=0.6,  message=FALSE, echo = FALSE, cache=TRUE, warning = FALSE, include=TRUE, fig.cap="Boxplots of dieldrin concentrations by treatment/week. Average values for T0 and T16 are shown."}

df <- data.frame(T0T16_avg = ((T0$Dieldrin + T16$Dieldrin) / 2), data %>% filter(Week == "T39") %>% select(Dieldrin), data %>% filter(Week == "T52") %>% select(Dieldrin), data %>% filter(Week == "T0") %>% select(Treatment), data %>% filter(Week == "T0") %>% select(SampleNo)  ) %>% rename(T39 = Dieldrin) %>%  rename(T52 = Dieldrin.1) 


mod <- lm(value ~ name, data = df %>% pivot_longer(cols = c("T0T16_avg", "T39", "T52")))
#summary(mod)

ggboxplot( data = df %>% pivot_longer(cols = c("T0T16_avg", "T39", "T52")), x = "Treatment", y = "value", fill = "name", palette = "simpsons", ylab = "Dieldrin (µg/g)") + rotate_x_text(angle = 45) + labs(fill = "Week")

```
<br/>
```{r lineplot, fig.width=8, fig.asp=0.7,  message=FALSE, echo = FALSE, cache=FALSE, warning = FALSE, fig.cap="Dieldrin concentrations (log) across time. Error bars show the standard error of the mean of four replicates."}

l0 <- data %>% filter(SampleName != "t0_4.run" ) %>% ggpubr::ggline(data = ., x = "Week_int", y = "Dieldrin_trans", ylab = "Dieldrin (log)", add = c("mean_se"), color = "Treatment", palette = "simpsons") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal")

#l01 <- data  %>% filter(SampleNo != 4 ) %>% ggline(data = ., x = "Week_int", y = "T0_Diff", add = c("mean_se"), color = "Treatment", palette = "simpsons") + rotate_x_text(angle = 45) + stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal")



pdf(NULL)
g1 <- ggpubr::ggarrange(l0, nrow = 1, ncol=1, common.legend = TRUE)
x = dev.off()
g1

```
<br/>
 
```{r line2, echo=FALSE, fig.width=8, fig.asp=1,  message=FALSE, cache=TRUE, warning = FALSE, fig.cap="Residues remaining since T0 in percent for two sets of treatments including the control (a,b). Error bars show the standard error of the mean of four replicates. Dieldrin concentrations (µg/g) over time."}

l1 <- data  %>% filter(SampleNo != 4 ) %>% filter(Week != "T52" ) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T0_Diff", ylab = "Residue remaining since T0 (%)", add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE)  + ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") + ggpubr::rotate_x_text(angle = 45) 

s1 <- data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week != "T52" ) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE ) + ggpubr::rotate_x_text(angle = 45)

l2 <-   data  %>% filter(SampleNo != 4 ) %>% filter(Week != "T52" ) %>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T0_Diff", ylab = c("Residue remaining since T0 (%)"), add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE) +  ggpubr::rotate_x_text(angle = 45)+ ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") 

s2 <-  data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week != "T52" )%>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE) + ggpubr::rotate_x_text(angle = 45)


pdf(NULL)
x = dev.off()
ggpubr::ggarrange(ncol =1, nrow=2, ggarrange(l1, s1, ncol = 2, nrow =1, common.legend = TRUE), ggarrange(l2, s2, ncol =2, nrow =1, common.legend = TRUE), labels = "auto" ) 

```
<br/>

```{r line23952, echo=FALSE, fig.width=8, fig.asp=1,  message=FALSE, cache=TRUE, warning = FALSE, fig.cap="Residues remaining since T39 (9 month) in percent for two sets of treatments including the control (a,b). Error bars show the standard error of the mean of four replicates. Dieldrin concentrations (µg/g) over time."}
l1 <- data  %>% filter(SampleNo != 4 ) %>% filter(Week %in% c("T39", "T52" )) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T39_Diff", ylab = c("Residue remaining since T39 (%)"), add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE)  + ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") + ggpubr::rotate_x_text(angle = 45) 

s1 <- data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week %in% c("T39", "T52" )) %>% filter(Treatment %in% c("Control", "Heat", "Lime", "Biochar", "PoultryLitter","H2O2")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE ) + ggpubr::rotate_x_text(angle = 45)

l2 <-   data  %>% filter(SampleNo != 4 ) %>% filter(Week %in% c("T39", "T52" )) %>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggline(data =., x = "Week_int", y = "T39_Diff", ylab = c("Residue remaining since T39 (%)"),  add = c("mean_se"), color = "Treatment", palette = "simpsons",xlab = FALSE) +  ggpubr::rotate_x_text(angle = 45)+ ggpubr::stat_compare_means(aes(group = Treatment), label = "p.signif", method = "kruskal") 

s2 <-  data  %>% filter(SampleName != "t0_4.run" ) %>% filter(Week %in% c("T39", "T52" ))%>% filter(Treatment %in% c("Control", "CitricAcid", "Inositol","SodiumFormate", "SodiumAcetate","FumaricAcid")) %>% ggpubr::ggscatter(data=., x = "Week_int", y = "Dieldrin", ylab = "Dieldrin (µg/g)", add = c("reg.line"), color = "Treatment", palette = "simpsons",xlab = FALSE) + ggpubr::rotate_x_text(angle = 45)

pdf(NULL)
x = dev.off()
ggpubr::ggarrange(ncol =1, nrow=2, ggarrange(l1, s1, ncol = 2, nrow =1, common.legend = TRUE), ggarrange(l2, s2, ncol =2, nrow =1, common.legend = TRUE), labels = "auto" ) 

```
<br/>

# Dieldrin loss
```{r dloss, echo=FALSE, fig.width=10, fig.asp=2, include=TRUE, fig.cap="Residues loss in percent. Error bars show the standard error of the mean of four replicates. Letters show differences of the mean after multiple comparison tests (dunn test, holm correct *p* value)."}
library(ggpubr)
library(agricolae)

#Loss plot for week 39
df <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T39" )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p1 <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T39" ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", facet.by = "Week", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%)") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 15) + geom_hline(yintercept = 0, linetype = 2)  + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)
#+ ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "Control", hide.ns = TRUE)

#Loss plot for week 52
df <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p2 <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", facet.by = "Week", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%)") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 23) + geom_hline(yintercept = 0, linetype = 2)  + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)
#+ ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "Control", hide.ns = TRUE)

## loss plot from week 52 since week 39 
df <-  data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" )
kr.test <- with(df,kruskal(loss39,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p3 <- data %>% filter(SampleNo != 4 ) %>% filter(Week == "T52" ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss39",  fill = "Treatment", palette = "simpsons", facet.by = "Week", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%) T39 - T52") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 23) + geom_hline(yintercept = 0, linetype = 2) + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)


## loss plot from week 39 using average values of T0 and T16 with dunn test labels
# Do not include - not sure about interpretation
df1 <- data.frame(T0T16_avg = ((T0$Dieldrin + T16$Dieldrin) / 2), data %>% filter(Week == "T39") %>% select(Dieldrin), data %>% filter(Week == "T52") %>% select(Dieldrin), data %>% filter(Week == "T0") %>% select(Treatment), data %>% filter(Week == "T0") %>% select(SampleNo)  ) %>% rename(T39 = Dieldrin) %>%  rename(T52 = Dieldrin.1) 

df <-  df1 %>% dplyr::mutate(loss = (T0T16_avg - T39) / T0T16_avg *100 )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
#dunntest.df <- rstatix::dunn_test(df, loss ~ Treatment)
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p4 <- df1 %>% dplyr::mutate(loss = (T0T16_avg - T39) / T0T16_avg *100 ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%) T0T16_avg - T39") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 10) + geom_hline(yintercept = 0, linetype = 2) + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)

#pwc <- df %>% mutate(loss = (T0T16_avg - T52) / T0T16_avg *100 ) %>% 
#  dunn_test(loss ~ Treatment, p.adjust.method = "holm") 

## loss plot from week 52 using average values of T0 and T16 with dunn test labels
# Do not include - not sure about interpretation
df1 <- data.frame(T0T16_avg = ((T0$Dieldrin + T16$Dieldrin) / 2), data %>% filter(Week == "T39") %>% select(Dieldrin), data %>% filter(Week == "T52") %>% select(Dieldrin), data %>% filter(Week == "T0") %>% select(Treatment), data %>% filter(Week == "T0") %>% select(SampleNo)  ) %>% rename(T39 = Dieldrin) %>%  rename(T52 = Dieldrin.1) 

df <-  df1 %>% dplyr::mutate(loss = (T0T16_avg - T52) / T0T16_avg *100 )
kr.test <- with(df,kruskal(loss,Treatment,group=TRUE, p.adj="holm"))
levels  <- levels(df$Treatment) %>% as.data.frame()
groups1 <- kr.test$groups %>% rownames_to_column("Treatment")
groups1 <- groups1[match(levels$., groups1$Treatment),]
label <- as.vector(groups1$groups)
p5 <- df1 %>% mutate(loss = (T0T16_avg - T52) / T0T16_avg *100 ) %>%  ggpubr::ggbarplot(data =., x = "Treatment", y = "loss",  fill = "Treatment", palette = "simpsons", legend = "none",add = c("mean_se"), lab.vjust = -2, xlab = FALSE, ylab = "Dieldrin loss (%) T0T16_avg - T52") + ggpubr::rotate_x_text(angle = 45) + ggpubr::stat_compare_means(method = "kruskal", label.y = 22) + geom_hline(yintercept = 0, linetype = 2) + annotate("text", x = groups1$Treatment, y=c(20,20,20,20,20,20,20,20,20,20,20), label = label)+ ggpubr::stat_compare_means(label = "..p.signif..", method = "t.test",  ref.group = "Control", hide.ns = TRUE)


ggarrange(p1, p2, p3, ncol = 1)



```


```{r ordinarymodels, message=FALSE, echo = TRUE, warning = FALSE, include=FALSE}

intercept <- 1
df <- data %>% filter(Week != "T0") %>% filter(SampleNo != 4 )
mod2 <- lm(I((T0_Diff) - intercept) ~  Treatment, data = df)
summary(mod2)
car::Anova(mod2, type = 3)

intercept <- data %>% filter(SampleName != "t0_4.run" ) %>% summarise(meanD = mean(Dieldrin))
intercept <- intercept$meanD
df <- data %>% filter(SampleName != "t0_4.run" )
mod3 <- lm(I(Dieldrin - intercept) ~ Treatment, data = df)
summary(mod3)
car::Anova(mod2, type = 3)

```

# Some awesome summary diagnostics
https://www.datanovia.com/en/lessons/repeated-measures-anova-in-r/
```{r rmanova, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=TRUE}
# Normality
library(rstatix)
data %>% filter(SampleName != "t0_4.run" ) %>% 
  group_by(Week) %>%
   rstatix::shapiro_test(Dieldrin)

# outliers
data  %>%
  group_by(Week) %>%
  rstatix::identify_outliers(Dieldrin) %>% select(Week,Treatment, Dieldrin, is.outlier, is.extreme)

# Summary mean and sd
data %>% filter(SampleName != "t0_4.run" ) %>%
  group_by(Week) %>%
  get_summary_stats(Dieldrin, type = "mean_sd")
```
Transform dieldrin values to improve distribution in order to meet normality assumption
remove 1 extreme outlier sample (Control, 1.33µg/g dieldrin)

```{r rmanova2, echo=FALSE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=TRUE}
data_fltrd %>%
  group_by(Week) %>%
   rstatix::shapiro_test(Dieldrin_trans) 

data_fltrd %>%
  group_by(Week) %>%
   rstatix::shapiro_test(Dieldrin) 
```
Go with log transform for now

```{r rmanova3, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=TRUE}
library(rstatix)

res.aov <- anova_test(data = data_fltrd, dv = Dieldrin_trans, between = c(Week, Treatment))

rstatix::get_anova_table(res.aov)

pwc <- data_fltrd %>%
  pairwise_t_test(
    Dieldrin_trans ~ Week, paired = FALSE,
    p.adjust.method = "bonferroni"
    )

bxp <- ggboxplot(data_fltrd, x = "Week", y = "Dieldrin_trans", add = "point")

pwc <- pwc %>% add_xy_position(x = "Week")
bxp <- bxp + 
  stat_pvalue_manual(pwc) +
  labs(
    subtitle = get_test_label(res.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)
  )
bxp
```

## Some more summary stats, this time including Treatment
```{r rmanova4, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE, include=FALSE}
data_fltrd %>%
  group_by(Treatment, Week) %>%
  get_summary_stats(Dieldrin_trans, type = "mean_sd")

data_fltrd %>%
  group_by(Treatment, Week) %>%
  identify_outliers(Dieldrin) %>% dplyr::select(Week, Treatment, Dieldrin, is.outlier, is.extreme)

ggqqplot(data_fltrd, "Dieldrin_trans", ggtheme = theme_bw()) +
  facet_grid(Week ~ Treatment, labeller = "label_both")
```

## A repeated measures ANOVA (this is not valid as I used replicates as individuals)
There were no individual soils that were treated differently but wanted to see what happens if we assume that each replicate was the same individual
```{r rmanova5, echo=TRUE, message=FALSE, echo = TRUE, cache=TRUE, warning = FALSE}
data_sel <- data %>% dplyr::select(Replicate, Treatment, Week, Dieldrin) %>% as_tibble()
anova_test(  data = data_sel, dv = Dieldrin, wid = Replicate,
  within = c(Treatment, Week) )

```


# LME models
```{r lme, fig.width=10, fig.asp= 1, message=FALSE, echo = TRUE, warning = FALSE}
library(lme4)
library(lmerTest)
library(car)
library(rafalib)
library(visreg)
library(sjPlot)
library(sciplot)
library(nlme)
library(MASS)
library(ggpubr)
theme_set(theme_bw())


M <- gls(log(Dieldrin) ~ Treatment, data = data_fltrd)
M0 <- lme(log(Dieldrin)  ~ Treatment,  random =~ 1 | SampleNo, data = data_fltrd)
M1 <- lme(log(Dieldrin)  ~ Treatment,  random =~ 1 | Week_int/SampleNo, data = data_fltrd)
M2 <- lme(log(Dieldrin)  ~  Treatment,  random =~ 1 | SampleNo/Week_int, data = data_fltrd)
M3 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | SampleNo/InjectionDate, data = data_fltrd)
M4 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | InjectionDate, data = data_fltrd)
M5 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | InjectionDate/SampleNo, data = data_fltrd)
M6 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | Week_int/InjectionDate, data = data_fltrd)
M7 <- lme(log(Dieldrin)  ~ Treatment,  random =~  1 | Week_int, data = data_fltrd)
anova(M, M0, M1, M2, M3, M4, M5, M6, M7)

M <- gls(log1p(Dieldrin) ~ Treatment + Week, data = data)
M0 <- lme(log1p(Dieldrin)  ~ Treatment + Week,  random =~ 1 | SampleNo, data = data)
M1 <- lme(log1p(Dieldrin)  ~ Treatment + Week,  random =~  1 | InjectionDate, data = data)
#M2 <- lme(log1p(Dieldrin_cor)  ~ Treatment + Week,  random =~  1 | Week_int, data = data)
anova(M, M0, M1)


M1 <-  lme(log(Dieldrin)  ~ Treatment,  random =~  1 | Week_int/InjectionDate, data = data_fltrd)

E <- resid(M1, type = 'normalized') 
shapiro.test(E)
E <- data.frame(E = E)

Ehist <- ggplot(E, aes(x=(E))) +  geom_histogram(color="black", fill="black") + ggtitle("Residuals Histogram")

F0 <- fitted(M1)
df <- data.frame(F0 = F0, E = E, Treatment = data_fltrd$Treatment, Week_int = data_fltrd$Week_int, Dieldrin = data_fltrd$Dieldrin_trans) 

residscatter <- ggscatter(data= df, x = "F0", y = "E", xlab = "Fitted values", ylab = "Residuals") + ggtitle("Residuals distribution")

D_scatter <- ggscatter(data= df, x = "Dieldrin", y = "E", xlab = "Dieldrin_trans", ylab = "Residuals", add = ("reg.line"))

trt_bxp <- ggboxplot(data= df, x = "Treatment", y = "E", xlab = "Treatment fitted values", ylab = "Residuals", add = ("jitter"))+ rotate_x_text(angle = 45)

Week_scatter <- ggscatter(data= df, x = "Week_int", y = "E", xlab = "Week_int", ylab = "Residuals", add = ("reg.line"))

ggarrange(Ehist, residscatter, D_scatter, Week_scatter, trt_bxp, nrow = 3, ncol = 2)
```
  
## Auto-correlation plot 
```{r}
acf(E)
```

```{r, message=FALSE, echo = FALSE, warning = FALSE}
summary(M1)
```
